---
format: 
  pdf:
    keep-tex: true
editor_options: 
  chunk_output_type: console
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#", fig.height = 3, 
  cache = FALSE,  collapse = TRUE,
  error = TRUE, echo = FALSE,
  message = FALSE, fig.width = 7
)
```

<!-- put your name below instead of mine -->

Caleb Skinner

Global Health Survey Questions 1-5

<!-- Setting up tidyverse. Reading in the csv and all that bonkers stuff -->
```{r}
#| include: false
library("here")
library("tidyverse"); theme_set(theme_minimal())
library(rstanarm)
library(scales)
library(ggpubr)
library(broom)
library(AICcmodavg)
library(waffle)
library(gtsummary)

# loading df- helpful for viewing the questions
file_name <- here("Global_Health_data.csv")
df0 <- read_csv(file_name) %>%
  select(20,22:24,26,28,30,36,38:45,47:50)

# removing excess rows and fixing bad responses
df <- df0[-c(1:2),] %>% 
  mutate(Q17 = recode(Q17,
                      'Strongly Agree ' = 'Strongly Agree',
                      'Undecided ' = 'Undecided',
                      'Strongly Disagree ' = 'Strongly Disagree'),
         Q22 = recode(Q22,
                      'Strongly Agree ' = 'Strongly Agree',
                      'Undecided ' = 'Undecided',
                      'Strongly Disagree ' = 'Strongly Disagree'),
         Q14 = recode(Q14,
                      'No ' = 'No'),
         Q13 = recode(Q13,
                      '15+ years ' = '15+ years',
                      '5 - 10 years ' = '5 - 10 years',
                      '10 - 15 years ' = '10 - 15 years',
                      '1 - 5 years ' = '1 - 5 years',
                      'Less than one year ' = 'Less than one year'
         ),
         Q6 = recode(Q6,
                     'Pre-professional track - only choose this option if you do not have another major that fits into one of the above categories' = 'Pre-Professional Track'),
         Q18 = recode(Q18,
                      'I don’t know' = "I don't know")
  )
```

## Questions:

## 1.  Describe the dataset: what do the respondents look like?

The following visualizations are meant to give a general understanding of the respondent pool.

<!-- Year in Undergraduate Program -->

```{r}
df %>% filter(Q2 != "") %>%
  group_by(Q2) %>%
  summarise(
    Count = n()
  ) %>% ggplot(aes(Q2, Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Respondents' Year in Undergraduate Program", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 3)
```

<!-- Age -->

```{r}
df %>% filter(Q3 != "") %>%
  group_by(Q3) %>%
  summarise(
    Count = n()
  ) %>% ggplot(aes(Q3, Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Respondents' Age", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 6)
```

<!-- Ethnicity -->

```{r}
df %>% filter(Q29 != "") %>%
  group_by(Q29) %>%
  summarise(
    Count = n()
  ) %>% ggplot(aes(reorder(Q29, -Count), Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Respondents' Ethnicity", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 5) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 13))
```


<!-- Gender Identity -->

```{r}
df %>% filter(Q9 != "") %>%
  group_by(Q9) %>%
  summarise(
    Count = n()
  ) %>% ggplot(aes(reorder(Q9, -Count), Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Respondents' Gender Identity", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 6) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 13))
```

<!-- Undergraduate University -->

```{r}
abc <- df %>% filter(Q4 != "") %>%
  group_by(Q4) %>%
  summarise(
    Count = n()
  ) %>%
  mutate(
    Small = if_else(Count < 2, 1, if_else(Q4 == "Other", 8, 0))
  )
abc %>%
  add_row(
    Q4 = "Other", Count = sum(abc$Small), Small = 0
  ) %>%
  filter(Small == 0) %>% 
  ggplot(aes(reorder(Q4, -Count), Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Respondents' Undergraduate University", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 5) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 10)) +
  theme(axis.text.x = element_text(size = 5.8))
```

<!-- Degree Type -->

```{r}
df %>% filter(Q5 != "") %>%
  group_by(Q5) %>%
  summarise(
    Count = n()
  ) %>% ggplot(aes(reorder(Q5, -Count), Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Respondents' Degree Type", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 5) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12))
```

<!-- Category of Major -->

```{r}
df %>% filter(Q6 != "") %>%
  group_by(Q6) %>%
  summarise(
    Count = n()
  ) %>% ggplot(aes(reorder(Q6, -Count), Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Respondents' Major", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 4) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 11)) +
  theme(axis.text.x = element_text(size = 8))
```
<!-- Born outside of the US -->

```{r}
df %>% filter(Q10 != "") %>%
  group_by(Q10) %>%
  summarise(
    Count = n()
  ) %>% ggplot(aes(Q10, Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Born Abroad?", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 6)
```

<!-- Lived outside of the US -->

```{r}
df %>% filter(Q12 != "") %>%
  group_by(Q12) %>%
  summarise(
    Count = n()
  ) %>% ggplot(aes(Q12, Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Lived Abroad?", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 6)
```

<!-- How long lived outside the US -->

```{r}
df %>% filter(Q13 != "") %>%
  group_by(Q13) %>%
  summarise(
    Count = n()
  ) %>% ggplot(aes(x = factor(Q13, level = c('Less than one year',
                                             '1 - 5 years',
                                             '5 - 10 years',
                                             '10 - 15 years',
                                             '15+ years')), Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Lived Abroad Length", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = .5) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 10))
```
\newpage

## 2. How do pre-medical students perceive a career in global health?

A. Overall Responses to pursuing a career in Global Health.
<!-- Q14 -->

```{r}
df14 <- df %>% 
  filter(Q14 != "") # %>% view()
# set yes = 1, unsure = .5, and no = 0 for t tests
df14ttest <- df14 %>%
  mutate(Q14 = case_when(
    Q14 == "Unsure" ~ .5,
    Q14 == "Yes" ~ 1,
    Q14 == "No" ~ 0)
  )

# Bar Graph
df14 %>%
  group_by(Q14) %>%
  summarise(
    Count = n()
  ) %>% ggplot(aes(Q14, Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Interested in a Global Health Career?", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 3)
```

\newpage

B. Pursuing a career in Global Health grouped by those who have lived abroad.

```{r}
df14 %>%
  filter(Q12 != "") %>% 
  group_by(Q12, Q14) %>%
  summarise(
    Count = n()
  ) %>%
  ggplot(aes(Q12, Count, fill = Q14)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Global Health Career Interest by Lived Abroad",
       x = "Lived Abroad?",
       fill = "Global Health Interest:",
       y = "") +
  theme(legend.position = "bottom") +
  geom_text(aes(label = signif(Count)), vjust = -.1,
            position = position_dodge(width = .9)) +
  scale_y_continuous(limits = c(0,70))
```

\newpage

The following is a t-test measuring the difference in interest in a Global Health Career in those who have lived outside the US and those who have not. For this t-test I counted "unsure" responses as 1/2 a "yes" and 1/2 a "no".
The results are significant. Those who have lived outside the US demonstrate a higher interest in a Global Health Career than those who have not lived outside the US.

```{r}
# t test of Career in Global Health by lived outside the US
# Keep unsure as .5
# results are significant. True difference of means is not equal to 0.
# p-value = .00035
# mean of not lived outside US: .622
# mean of lived outside US: .845
t.test(df14ttest %>% filter(Q12 == "No") %>% select(Q14),
       df14ttest %>% filter(Q12 == "Yes") %>% select(Q14))
```

The following is also a t-test measuring the difference in interest in a Global Health Career in those who have lived outside the US and those who have not. For this t-test I removed "unsure" responses from the data.
Once again, the results are significant. Those who have lived outside the US demonstrate a higher interest in a Global Health Career than those who have not lived outside the US.

```{r}
# Remove unsure observations
# results are significant. True difference of means is not equal to 0.
# p-value = .00102
# mean of not lived outside US: .722
# mean of lived outside US: .955
t.test(df14ttest %>% filter(Q12 == "No", Q14 != .5) %>% select(Q14),
       df14ttest %>% filter(Q12 == "Yes", Q14 != .5) %>% select(Q14))
```

\newpage

```{r}
# How long lived outside the US
df14 %>%
  filter(Q13 != "") %>% 
  group_by(Q13, Q14) %>%
  summarise(
    Count = n()
  ) %>%
  ggplot(aes(Q13, Count, fill = Q14)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Global Health Career Interest by length of time abroad",
       x = "Time Abroad?",
       fill = "Global Health Interest:",
       y = "") +
  theme(legend.position = "bottom") +
  geom_text(aes(label = signif(Count)), vjust = -.1,
            position = position_dodge(width = .9)) +
  scale_y_continuous(limits = c(0,6.5))
```

\newpage

C. Pursuing a career in Global Health grouped by those who were born abroad.

```{r}
df14 %>%
  filter(Q10 != "") %>% 
  group_by(Q10, Q14) %>%
  summarise(
    Count = n()
  ) %>%
  ggplot(aes(Q10, Count, fill = Q14)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Global Health Career Interest by Born Abroad",
       x = "Born Abroad?",
       fill = "Global Health Interest:",
       y = "") +
  theme(legend.position = "bottom") +
  geom_text(aes(label = signif(Count)), vjust = -.2,
            position = position_dodge(width = .9)) +
  scale_y_continuous(limits = c(0,70))
```

\newpage

The following is a t-test measuring the difference in interest in a Global Health Career in those who were born outside the US and those who were not. For this t-test I counted "unsure" responses as 1/2 a "yes" and 1/2 a "no".
The results are significant. Those who were born outside the US demonstrate a higher interest in a Global Health Career than those who were not born outside the US.

```{r}
# t test of Career in Global Health by born outside the US
# Keep unsure as .5
# results are significant. True difference of means is not equal to 0.
# p-value = .00042
# mean of not lived outside US: .630
# mean of lived outside US: .857
t.test(df14ttest %>% filter(Q10 == "No") %>% select(Q14),
       df14ttest %>% filter(Q10 == "Yes") %>% select(Q14))
```

The following is a t-test measuring the difference in interest in a Global Health Career in those who were born outside the US and those who were not. For this t-test I removed "unsure" responses.
The results are significant. Those who were born outside the US demonstrate a higher interest in a Global Health Career than those who were not born outside the US.

```{r}

# t test of Career in Global Health by born outside the US
# remove unsure values
# results are significant. True difference of means is not equal to 0.
# p-value = .00
# mean of not lived outside US: .729
# mean of lived outside US: 1.0000
t.test(df14ttest %>% filter(Q10 == "No", Q14 != .5) %>% select(Q14),
       df14ttest %>% filter(Q10 == "Yes", Q14 != .5) %>% select(Q14))
```

\newpage

D. Pursuing a career in Global Health grouped by major.

```{r}
df14 %>%
  filter(Q6 != "") %>% 
  group_by(Q6, Q14) %>%
  summarise(
    Count = n()
  ) %>%
  ggplot(aes(Q6, Count, fill = Q14)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Global Health Career Interest by Major", x = "",
       fill = "Global Health Interest:",
       y = "") +
  theme(legend.position = "bottom", axis.text.x = element_text(size = 6.7)) +
  geom_text(aes(label = signif(Count)), vjust = -.1,
            position = position_dodge(width = .9)) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 11)) +
  scale_y_continuous(limits = c(0,40))
```

\newpage

## 3. Which aspects of the global health field interest you when considering your medical career?

A. Total Results of Aspects of Global Health Field Considered

```{r}
df15 <- df14 %>% filter(Q23 != "" & !is.na(Q15)) %>% mutate(
  "Health Equity" = str_count(Q15, "Health equity"),
  "Public Health" = str_count(Q15, "Public health"),
  "Travel Opportunities" = str_count(Q15, "Travel opportunities"),
  "Provide for Underserved Communities" = str_count(Q15, "Want to provide healthcare to underserved communities"),
  "Uninterested" = str_count(Q15, "Not interested in the global health field"),
  "Research Opportunities" = str_count(Q15, "Research opportunities"),
  "Non-Profit/Healthcare Admin" = str_count(Q15, "Non-profit and healthcare administration"),
  "Cross-Cultural Experiences" = str_count(Q15, "Cross-cultural experiences"),
  "Number_of_Fields_Selected" = str_count(Q15, ",") + 1 - str_count(Q15, "Not interested in the global health field")
) # %>% view()

# creates a tibble of the totals
df15g <- tibble(
  "Fields" = c("Health Equity", "Public Health", "Travel Opportunities", 
               "Provide for Underserved Communities", "Uninterested",
               "Research Opportunities", 
               "Non-Profit/Healthcare Admin","Cross-Cultural Experiences"),
  "Interested" = c(sum(df15$`Health Equity`), sum(df15$`Public Health`), sum(df15$`Travel Opportunities`),
                   sum(df15$`Provide for Underserved Communities`), sum(df15$`Uninterested`),
                   sum(df15$`Research Opportunities`), sum(df15$`Non-Profit/Healthcare Admin`),
                   sum(df15$`Cross-Cultural Experiences`))) %>%
  mutate(
    "Uninterested" = nrow(df15) - Interested,
    "Percent" = percent((Interested / nrow(df15)), accuracy = .1)
  ) # %>% view()

# creates a barplot of each of the Global Health Interest Fields
# and includes percent selected
ggplot(df15g, aes(reorder(Fields, -Interested), Interested)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Interest in Global Health Fields", x = "", y = "") +
  geom_text(aes(label = Percent), nudge_y = 5) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  theme(axis.text.x = element_text(size = 7.5))
```

```{r}
df15 %>% group_by(Number_of_Fields_Selected) %>%
  summarise(
    Count = n()
  ) %>% 
  ggplot(aes(Number_of_Fields_Selected, Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Interest in Global Health Fields",
       x = "Total Fields Selected",
       y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 1)
```

\newpage

B. Results by Lived Outside the US

```{r}
# converts the list into several columns
df15Lived <- df15 %>% filter(Q12 == "Yes") # %>% view()
df15NotLived <- df15 %>% filter(Q12 == "No") # %>% view()

# creates a tibble of the totals
df15gLive <- tibble(
  "Fields" = c("Health Equity", "Health Equity", "Public Health", "Public Health",
               "Travel Opportunities", "Travel Opportunities", "Provide for Underserved Communities",
               "Provide for Underserved Communities", "Uninterested", "Uninterested","Research Opportunities", 
               "Research Opportunities","Non-Profit/Healthcare Admin","Non-Profit/Healthcare Admin",
               "Cross-Cultural Experiences", "Cross-Cultural Experiences"),
  Lived_Abroad = c("Yes", "No", "Yes", "No","Yes", "No","Yes", "No",
                   "Yes", "No","Yes", "No","Yes", "No","Yes", "No"),
  "Interested" = c(sum(df15Lived$`Health Equity`), sum(df15NotLived$`Health Equity`),
                   sum(df15Lived$`Public Health`), sum(df15NotLived$`Public Health`),
                   sum(df15Lived$`Travel Opportunities`),
                   sum(df15NotLived$`Travel Opportunities`),
                   sum(df15Lived$`Provide for Underserved Communities`),
                   sum(df15NotLived$`Provide for Underserved Communities`),
                   sum(df15Lived$`Uninterested`),sum(df15NotLived$`Uninterested`),
                   sum(df15Lived$`Research Opportunities`),
                   sum(df15NotLived$`Research Opportunities`),
                   sum(df15Lived$`Non-Profit/Healthcare Admin`),
                   sum(df15NotLived$`Non-Profit/Healthcare Admin`),
                   sum(df15Lived$`Cross-Cultural Experiences`),
                   sum(df15NotLived$`Cross-Cultural Experiences`))
) %>% mutate(
  Decimal = as.double(if_else(Lived_Abroad == "Yes", Interested/nrow(df15Lived), Interested/nrow(df15NotLived))),
  Percent = percent(Decimal,accuracy = .1)
) # %>% view()

# creates a barplot of each of the Global Health Interest Fields and Compares
# Lived in US to not Lived in US
# TOTALS
ggplot(df15gLive, aes(reorder(Fields, -Interested), Interested, fill = Lived_Abroad)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Interest in Global Health Fields",
       x = "", fill = "Lived Abroad?", y = "") +
  geom_text(aes(label = Interested), vjust = -.2, position = position_dodge(width = .9)) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(limits = c(0,120)) +
  theme(axis.text.x = element_text(size = 6.7))
```

```{r}
ggplot(df15gLive, aes(reorder(Fields, -Decimal), Decimal, fill = Lived_Abroad)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Respondents' interest in the following Global Health Fields",
       x = "", fill = "Lived Abroad?", y = "") +
  geom_text(aes(label = Percent), vjust = -.3,
            position = position_dodge(width = .9), size = 1.8) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1)
  ) +
  theme(axis.text.x = element_text(size = 6.7))
```

\newpage

Below is a Chi Squared Test. This tests to see if the two distributions of interest in the global health fields are distinct from one another. The test cannot confirm that there is a distinction. In other words, the difference in interest of the various global health fields of those who lived abroad and those who did not live abroad is not significant.

```{r}
#| warning: false
df15gLiveChi <- df15gLive %>% select(Fields, Lived_Abroad, Percent) %>% 
  pivot_wider(names_from = Lived_Abroad, values_from = Percent)
chisq.test(df15gLiveChi$Yes, df15gLiveChi$No)
```

```{r}
full_join(df15Lived %>% 
            group_by(Number_of_Fields_Selected) %>% 
            summarise(Yes = n()/nrow(df15Lived)), 
          df15NotLived %>% group_by(Number_of_Fields_Selected) %>% 
            summarise(No = n()/nrow(df15NotLived))) %>% pivot_longer(
              c(`Yes`, `No`), names_to = "Lived_Abroad", values_to = "Count") %>% mutate(
                Percent = percent(Count, accuracy= .01)) %>%
  ggplot(aes(Number_of_Fields_Selected, Count, fill = Lived_Abroad)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Total Fields Interested", x = "Total Fields Selected", 
       y= "", fill = "Lived Abroad") +
  geom_text(aes(label = Percent), vjust = -.3, position = position_dodge(width = .9), size = 1.7) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .05),
    labels = label_percent(accuracy = 1)
  ) +
  theme(axis.text.x = element_text(size = 8))
```

Below is a second Chi Squared Test. This tests to see if the two distributions are distinct from one another. The test cannot confirm that there is a distinction. In other words, the difference between the number of fields selected between those who lived abroad and did not live abroad is insignificant.

```{r}
#| warning: false
df15gLiveChiTotals <- full_join(df15Lived %>% 
                                  group_by(Number_of_Fields_Selected) %>% 
                                  summarise(Yes = n()/nrow(df15Lived)), 
                                df15NotLived %>% group_by(Number_of_Fields_Selected) %>% 
                                  summarise(No = n()/nrow(df15NotLived))) # %>% view()
chisq.test(df15gLiveChiTotals$Yes, df15gLiveChiTotals$No)
```

\newpage

C. Results by born outside the US

```{r}
# converts the list into several columns
df15Born <- df15 %>% filter(Q10 == "Yes") #%>% view()
df15NotBorn <- df15 %>% filter(Q10 == "No") #%>% view()

# creates a tibble of the totals
df15gBorn <- tibble(
  "Fields" = c("Health Equity", "Health Equity", "Public Health", "Public Health",
               "Travel Opportunities", "Travel Opportunities", "Provide for Underserved Communities",
               "Provide for Underserved Communities", "Uninterested", "Uninterested","Research Opportunities", 
               "Research Opportunities","Non-Profit/Healthcare Admin","Non-Profit/Healthcare Admin",
               "Cross-Cultural Experiences", "Cross-Cultural Experiences"),
  Born_Abroad = c("Yes", "No", "Yes", "No","Yes", "No","Yes", "No",
                  "Yes", "No","Yes", "No","Yes", "No","Yes", "No"),
  "Interested" = c(sum(df15Born$`Health Equity`), sum(df15NotBorn$`Health Equity`),
                   sum(df15Born$`Public Health`), sum(df15NotBorn$`Public Health`),
                   sum(df15Born$`Travel Opportunities`), sum(df15NotBorn$`Travel Opportunities`),
                   sum(df15Born$`Provide for Underserved Communities`), sum(df15NotBorn$`Provide for Underserved Communities`),
                   sum(df15Born$`Uninterested`),sum(df15NotBorn$`Uninterested`),
                   sum(df15Born$`Research Opportunities`), sum(df15NotBorn$`Research Opportunities`),
                   sum(df15Born$`Non-Profit/Healthcare Admin`), sum(df15NotBorn$`Non-Profit/Healthcare Admin`),
                   sum(df15Born$`Cross-Cultural Experiences`), sum(df15NotBorn$`Cross-Cultural Experiences`))
) %>% mutate(
  Decimal = as.double(if_else(Born_Abroad == "Yes", Interested/nrow(df15Born), Interested/nrow(df15NotBorn))),
  Percent = percent(Decimal,accuracy = .1)
) # %>% view()

# creates a barplot of each of the Global Health Interest Fields and Compares
# Lived in US to not Lived in US
# TOTALS
ggplot(df15gBorn, aes(reorder(Fields, -Interested), Interested, fill = Born_Abroad)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Interest in Global Health Fields",
       x = "", fill = "Born Abroad?", y = "") +
  geom_text(aes(label = Interested), vjust = -.1,
            position = position_dodge(width = .9), size = 3) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(limits = c(0,105)) +
  theme(axis.text.x = element_text(size = 6.7))
```

```{r}
ggplot(df15gBorn, aes(reorder(Fields, -Decimal), Decimal, fill = Born_Abroad)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Interest in Global Health Fields",
       x = "", fill = "Born Abroad?", y = "") +
  geom_text(aes(label = Percent), vjust = -.3, position = position_dodge(width = .9),
            size = 2.4) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1)
  ) +
  theme(axis.text.x = element_text(size = 6.7))
```

\newpage

Below is a Chi Squared Test. This tests to see if the two distributions of fields are distinct from one another. The test cannot confirm that there is a distinction. In other words, the difference in interest of the various global health fields of those who were born abroad and those who were not born abroad is not significant.

```{r}
#| warning: false
df15gBornChi <- df15gBorn %>% select(Fields, Born_Abroad, Percent) %>% 
  pivot_wider(names_from = Born_Abroad, values_from = Percent) # %>% view()
chisq.test(df15gBornChi$Yes, df15gBornChi$No)
```

```{r}
#| warning: false
full_join(df15Born %>% 
            group_by(Number_of_Fields_Selected) %>% 
            summarise(Yes = n()/nrow(df15Born)), 
          df15NotBorn %>% group_by(Number_of_Fields_Selected) %>% 
            summarise(No = n()/nrow(df15NotBorn))) %>% pivot_longer(
              c(`Yes`, `No`), names_to = "Born_Abroad", values_to = "Count") %>% mutate(
                Percent = percent(Count, accuracy= .01)) %>%
  ggplot(aes(Number_of_Fields_Selected, Count, fill = Born_Abroad)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Total Interested Fields", x = "Fields Selected", 
       y= "", fill = "Born Abroad") +
  geom_text(aes(label = Percent), vjust = -.3,
            position = position_dodge(width = .9), size = 2.2) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .05),
    labels = label_percent(accuracy = 1)
  )
```

Below is a Chi Squared Test. This tests to see if the two distributions of the number of fields selected are distinct from one another. The test cannot confirm that there is a distinction. In other words, the difference in the total number of fields interested in by those who were born abroad and those who were not born abroad is not significant.

```{r}
#| warning: false
df15gBornChiTotals <- full_join(df15Born %>%
                                  group_by(Number_of_Fields_Selected) %>%
                                  summarise(Yes = n()/nrow(df15Born)),
                                df15NotLived %>% group_by(Number_of_Fields_Selected) %>%
                                  summarise(No = n()/nrow(df15NotBorn))) # %>% view()
chisq.test(df15gBornChiTotals$Yes, df15gBornChiTotals$No)
```

\newpage

## 4. In your opinion, in addition to clinical training, physicians who work within global health (domestic or international) should have educational training in which THREE academic disciplines?

A. Overall Results of educational training

```{r}
# converts the list into several columns
df16 <- df %>% filter(Q16 != "") %>% mutate(
  Economics = str_count(Q16, "Economics"),
  Business = str_count(Q16, "Business"),
  Law = str_count(Q16, "Law"),
  Anthropology = str_count(Q16, "Anthropology"),
  'Policy Advocacy' = str_count(Q16, "Policy and Advocacy"),
  'Public Health' = str_count(Q16, "Public Health"),
  Sociology = str_count(Q16, "Sociology"),
  Language = str_count(Q16, "Language"),
  Ethics = str_count(Q16, "Ethics"),
  Total_Academic_Disciplines = str_count(Q16, ",") + 1
) # %>% view()

# creates a tibble of the totals
df16g <- tibble(
  Disciplines = c("Economics", "Business", "Law", "Anthropology", "Policy Advocacy",
                  "Public Health", "Sociology", "Language", "Ethics"),
  Preferred = c(sum(df16$Economics), sum(df16$Business), sum(df16$Law), sum(df16$Anthropology),
                sum(df16$'Policy Advocacy'), sum(df16$'Public Health'),
                sum(df16$Sociology), sum(df16$Language),
                sum(df16$Ethics))) %>%
  mutate(
    "Uninterested" = nrow(df16) - Preferred,
    "Percent" = percent((Preferred / nrow(df16)), accuracy = .1)
  ) #%>% view()

# creates a barplot of each of the academic disciplines for education training
# and includes percent selected
ggplot(df16g, aes(reorder(Disciplines, -Preferred), Preferred)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Important Academic Disciplines", x = "", y = "") +
  geom_text(aes(label = Percent), nudge_y = 5.5) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  theme(axis.text.x = element_text(size = 7.5))
```

```{r}
# total number of selections for respondent
df16 %>% group_by(Total_Academic_Disciplines) %>%
  summarise(
    Count = n()
  ) %>% 
  ggplot(aes(Total_Academic_Disciplines, Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Total Academic Disciplines Selected",
       x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 2) +
  scale_x_continuous(breaks = seq(1,9, by = 1))
```

\newpage

B. Relationship of preferred educational training with stated interest in Global Health

```{r}
df16Int <- df16 %>% filter(Q14 == "Yes") #%>% view()
df16NotInt <- df16 %>% filter(Q14 == "No") #%>% view()
df16UnsureInt <- df16 %>% filter(Q14 == "Unsure") #%>% view()

df16gInt <- tibble(
  Disciplines = c("Economics", "Economics", "Economics", "Business", "Business", 
                  "Business", "Law", "Law", "Law", "Anthropology", "Anthropology", 
                  "Anthropology", "Policy Advocacy", "Policy Advocacy", "Policy Advocacy",
                  "Public Health", "Public Health", "Public Health", "Sociology",
                  "Sociology", "Sociology", "Language", "Language", "Language",
                  "Ethics", "Ethics", "Ethics"),
  GH_Interest = c("Yes", "No", "Unsure", "Yes", "No", "Unsure", "Yes", "No", "Unsure",
                  "Yes", "No", "Unsure", "Yes", "No", "Unsure", "Yes", "No", "Unsure",
                  "Yes", "No", "Unsure", "Yes", "No", "Unsure", "Yes", "No", "Unsure"),
  Preferred = c(sum(df16Int$Economics),sum(df16NotInt$Economics),sum(df16UnsureInt$Economics),
                sum(df16Int$Business),sum(df16NotInt$Business),sum(df16UnsureInt$Business),
                sum(df16Int$Law),sum(df16NotInt$Law),sum(df16UnsureInt$Law),
                sum(df16Int$Anthropology),sum(df16NotInt$Anthropology),sum(df16UnsureInt$Anthropology),
                sum(df16Int$'Policy Advocacy'),sum(df16NotInt$'Policy Advocacy'),sum(df16UnsureInt$'Policy Advocacy'),
                sum(df16Int$'Public Health'),sum(df16NotInt$'Public Health'),sum(df16UnsureInt$'Public Health'),
                sum(df16Int$Sociology),sum(df16NotInt$Sociology),sum(df16UnsureInt$Sociology),
                sum(df16Int$Language),sum(df16NotInt$Language),sum(df16UnsureInt$Language),
                sum(df16Int$Ethics),sum(df16NotInt$Ethics),sum(df16UnsureInt$Ethics)
  )
) %>% mutate(
  Decimal = as.double(if_else(GH_Interest == "Yes", Preferred/nrow(df16Int), 
                              if_else(GH_Interest == "No", Preferred/nrow(df16NotInt), Preferred/nrow(df16UnsureInt)))),
  Percent = percent(Decimal,accuracy = .1)
) # %>% view()

# creates a barplot of each of the Academic Disciplines and Compares
# Interested in Global Health to not Interested
# TOTALS
ggplot(df16gInt, aes(reorder(Disciplines, -Preferred), Preferred, fill = GH_Interest)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Preferred Academic Disciplines", x = "",
       fill = "Global Health Interest", y = "") +
  geom_text(aes(label = Preferred), vjust = -.2,
            position = position_dodge(width = .9),size = 2.4) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  theme(axis.text.x = element_text(size = 6))
```

```{r}
ggplot(df16gInt, aes(reorder(Disciplines, -Decimal), Decimal, fill = GH_Interest)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Academic Discipline's selection Frequency",
       x = "", fill = "Global Health Interest", y = "") +
  geom_text(aes(label = Percent), vjust = -.3,
            position = position_dodge(width = .9), size = 1.7) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  theme(axis.text.x = element_text(size = 6)) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1)
  )
```

\newpage

Below is a Chi Squared Test. This tests to see if the distribution of the preference of academic disciplines preferred for global health is distinct when separated by respondent's stated interest in Global Health. The test cannot confirm that there is a distinction. In other words, the difference in preference of the academic disciplines of those who are interested in global health and who are not interested in global health is not statistically significant.

```{r}
#| warning: false
df16gIntChi <- df16gInt %>% select(Disciplines, GH_Interest, Percent) %>% 
  pivot_wider(names_from = GH_Interest, values_from = Percent) # %>% view()
chisq.test(df16gIntChi$Yes, df16gIntChi$No)
```

\newpage

C. Correlation of preferred educational training with major

```{r}
# refiltering out the data
df16major <- df16 %>% mutate(
  Economics = replace(Economics,Economics == 1, "Economics"),
  Business = replace(Business,Business == 1, "Business"),
  Law = replace(Law,Law == 1, "Law"),
  Anthropology = replace(Anthropology,Anthropology == 1, "Anthropology"),
  'Policy Advocacy' = replace('Policy Advocacy','Policy Advocacy' == 1, "Policy_Advocacy"),
  'Public Health' = replace('Public Health','Public Health' == 1, "Public_Health"),
  Sociology = replace(Sociology,Sociology == 1, "Sociology"),
  Language = replace(Language,Language == 1, "Language"),
  Ethics = replace(Ethics,Ethics == 1, "Ethics")
) %>% pivot_longer(c(Economics, Business, Law, Anthropology, 'Policy Advocacy',
                     'Public Health', Sociology, Language, Ethics), 
                   names_to = "Academic_Disciplines", values_to = "Disciplines") %>%
  filter(Disciplines != 0, Q6 != "") %>% select(-Q23, -Academic_Disciplines) # %>% view()

totalsmajor <- df16major %>% group_by(Q6) %>% summarise(
  Totals = n()
) # %>% view()

df16majorp <- df16major %>% group_by(Q6, Disciplines) %>% summarise(
  Count = n()
) %>% group_by(Q6) %>%
  mutate("Percent" = Count/sum(Count)) # %>% view()

# Total Count of Disciplines by Major
ggplot(df16majorp, aes(Q6, Count, fill = Disciplines)) +
  geom_bar(stat = "identity", position = "dodge") +
  guides(fill = guide_legend(reverse = TRUE)) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  labs(x = "Major", title = "Preferred Educational Training", y = "") +
  theme(axis.text.x = element_text(size = 6.5))
```

```{r}
ggplot(df16majorp, aes(reorder(Q6, -Count), Percent, fill = Disciplines)) +
  geom_bar(stat = "identity", position = position_stack(reverse = TRUE)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  labs(x = "Major", title = "Proportion of each Academic Discipline", y = "") +
  theme(axis.text.x = element_text(size = 6.5)) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1)
  )
```

\newpage

## 5. Should all pre-medical students take at least one global health-focused class before entering medical school?

A. Overall Results of Global Health Class Requirement

```{r}
Response_levels <- c("Strongly Agree", "Agree", "Undecided", "Disagree", "Strongly Disagree")

df17 <- df %>% 
  filter(Q17 != "") %>%
  mutate(
    factor(Q17, levels = Response_levels)
  ) #%>% view()

# Bar Graph
df17 %>%
  group_by(Q17) %>%
  summarise(
    Count = n()
  ) %>% 
  ggplot(aes(fct_relevel(Q17, Response_levels), Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Require a Global Health Course?", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 3)
```

\newpage

B. Global Health Class Requirement by Global Health Career Interest

```{r}
df17gInt <- df17 %>%
  filter(Q14 != "") %>% 
  group_by(Q14, Q17) %>%
  summarise(
    Count = n()
  ) # %>% view()
ggplot(df17gInt, aes(Q14, Count, fill = fct_relevel(Q17, Response_levels))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Required Global Health Course by Global Health Interest",
       x = "Global Health Career Interest",
       fill = "Require Course:", y ="") +
  theme(legend.position = "bottom", legend.title = element_text(size = 7.8),
        legend.text = element_text(size = 7.8)) +
  geom_text(aes(label = signif(Count)), vjust = -.1,
            position = position_dodge(width = .9)) +
  scale_y_continuous(limits = c(0, 45))
```

```{r}
df17gInt %>% group_by(Q14) %>%
  mutate(
    Decimal = Count / sum(Count),
    Percent = percent(Decimal, accuracy = .1)
  ) %>%
  ggplot(aes(Q14, Decimal, fill = fct_relevel(Q17, Response_levels))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Required Global Health Course by Global Health Interest",
       x = "Global Health Career Interest",
       fill = "Require Course:", y = "") +
  theme(legend.position = "bottom", legend.title = element_text(size = 7.8),
        legend.text = element_text(size = 7.8)) +
  geom_text(aes(label = Percent), vjust = -.2,
            position = position_dodge(width = .9), size = 2.9) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1)
  )
```


\newpage

C. Global Health Class Requirement by Living Abroad

```{r}
df17gAbroad <- df17 %>%
  filter(Q12 != "") %>% 
  group_by(Q12, Q17) %>%
  summarise(
    Count = n()
  ) # %>% view()
ggplot(df17gAbroad, aes(Q12, Count, fill = fct_relevel(Q17, Response_levels))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Required Global Health Course by Lived Abroad",
       x = "Lived Abroad", y = "",
       fill = "Require Course:") +
  theme(legend.position = "bottom", legend.title = element_text(size = 7.8),
        legend.text = element_text(size = 7.8)) +
  geom_text(aes(label = signif(Count)), vjust = -.1,
            position = position_dodge(width = .9)) +
  scale_y_continuous(limits = c(0, 65))
```

```{r}
df17gAbroad %>% group_by(Q12) %>%
  mutate(
    Decimal = Count / sum(Count),
    Percent = percent(Decimal, accuracy = .1)
  ) %>%
  ggplot(aes(Q12, Decimal, fill = fct_relevel(Q17, Response_levels))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Required Global Health Course by Lived Abroad",
       x = "Lived Abroad",
       fill = "Require Course:", y = "") +
  theme(legend.position = "bottom", legend.title = element_text(size = 7.8),
        legend.text = element_text(size = 7.8)) +
  geom_text(aes(label = Percent), vjust = -.1,
            position = position_dodge(width = .9), size = 3) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1),
    limits = c(0,.5)
  )
```

\newpage

D. Global Health Class Requirement by Major

```{r}
df17gMajor <- df17 %>%
  filter(Q6 != "") %>% 
  group_by(Q6, Q17) %>%
  summarise(
    Count = n()
  )
ggplot(df17gMajor, aes(Q6, Count, fill = fct_relevel(Q17, Response_levels))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Required Global Health Course", x = "Major",
       fill = "Require Course:", y = "") +
  theme(legend.position = "bottom", axis.text.x = element_text(size = 7),
        legend.title = element_text(size = 7.8), legend.text = element_text(size = 7.8)) +
  geom_text(aes(label = signif(Count)), vjust = -.2,
            position = position_dodge(width = .9), size = 2.8) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(limits = c(0,35))
```

```{r}
df17gMajor %>% group_by(Q6) %>%
  mutate(
    Decimal = Count / sum(Count),
    Percent = percent(Decimal, accuracy = .1)
  ) %>%
  ggplot(aes(reorder(Q6, -Count), Decimal, fill = fct_relevel(Q17, Response_levels))) +
  geom_bar(stat = "identity", position = position_stack()) +
  #guides(fill = guide_legend(reverse = FALSE)) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 11)) +
  labs(x = "Major", title = "Required Global Health by Major",
       fill = "Require Course:", y = "") +
  theme(axis.text.x = element_text(size = 6.5),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1),
  )
```


