---
format: 
  pdf:
    keep-tex: true
editor_options: 
  chunk_output_type: console
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#", fig.height = 3, 
  cache = FALSE,  collapse = TRUE,
  error = TRUE, echo = FALSE,
  message = FALSE
)
```

<!-- put your name below instead of mine -->

Caleb Skinner

Global Health Survey Questions 11-15

<!-- Setting up tidyverse. Reading in the csv and all that bonkers stuff -->
```{r}
#| include: false
library("here")
library("tidyverse"); theme_set(theme_minimal())
library(rstanarm)
library(scales)
library(ggpubr)
library(broom)
library(AICcmodavg)
library(waffle)
library(gtsummary)

# loading df- helpful for viewing the questions
file_name <- here("Global_Health_data.csv")
df0 <- read_csv(file_name) %>%
  select(20,22:24,26,28,30,36,38:45,47:74) %>% view()
# The ranked ones are from 51-72

# removing excess rows and fixing bad responses
df <- df0[-c(1:2),] %>% 
  mutate(Q17 = recode(Q17,
                      'Strongly Agree ' = 'Strongly Agree',
                      'Undecided ' = 'Undecided',
                      'Strongly Disagree ' = 'Strongly Disagree'),
         Q22 = recode(Q22,
                      'Strongly Agree ' = 'Strongly Agree',
                      'Undecided ' = 'Undecided',
                      'Strongly Disagree ' = 'Strongly Disagree'),
         Q14 = recode(Q14,
                      'No ' = 'No'),
         Q13 = recode(Q13,
                      '15+ years ' = '15+ years',
                      '5 - 10 years ' = '5 - 10 years',
                      '10 - 15 years ' = '10 - 15 years',
                      '1 - 5 years ' = '1 - 5 years',
                      'Less than one year ' = 'Less than one year'
         ),
         Q6 = recode(Q6,
                     'Pre-professional track - only choose this option if you do not have another major that fits into one of the above categories' = 'Pre-Professional Track'),
         Q18 = recode(Q18,
                      'I don’t know' = "I don't know")
  )
```

## Questions:

## 11. In your opinion, what are the greatest barriers to providing healthcare in low-resource settings?

A. Overall Results for Barriers to Providing Healthcare to Low-Resource Settings

```{r}
df23 <- df %>%
  filter(Q23 != "") %>%
  mutate(
    "Physician Supply" = str_count(Q23, "Physician supply"),
    "Lack of Equipment" = str_count(Q23, "Lack of medical equipment"),
    "Lack of Payment" = str_count(Q23, "Lack of health insurance"),
    "Lack of Patient Education" = str_count(Q23, "Lack of patient education"),
    "Language Barriers" = str_count(Q23, "Language barriers"),
    "Transportation Barriers" = str_count(Q23, "Transportation barriers"),
    "Infrastructure" = str_count(Q23, "Infrastructure"),
    "Number of Fields Selected" = str_count(Q23, ",") + 1
  )

# creates a tibble of the totals
df23g <- tibble(
  "Barriers" = c("Physician Supply", "Lack of Equipment",
               "Lack of Payment", "Lack of Patient Education",
               "Language Barriers", "Transportation Barriers",
               "Infrastructure"),
  "Votes" = c(sum(df23$`Physician Supply`),
              sum(df23$`Lack of Equipment`),
              sum(df23$`Lack of Payment`),
              sum(df23$`Lack of Patient Education`),
              sum(df23$`Language Barriers`),
              sum(df23$`Transportation Barriers`),
              sum(df23$`Infrastructure`))) %>%
  mutate(
    "Unselected" = nrow(df23) - Votes,
    "Percent" = percent((Votes / nrow(df23)), accuracy = .1)
  )
# creates a barplot of each of the perceived barriers to Global Health
# and includes percent selected
ggplot(df23g, aes(reorder(Barriers, -Votes), Votes)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Barriers to healthcare in low-resource settings",
       x = "", y = "") +
  geom_text(aes(label = Percent), nudge_y = 5) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  theme(axis.text.x = element_text(size = 7.3)) +
  scale_y_continuous(limits = c(0,120))
```

\newpage

B. Barriers to Providing Healthcare by Global Health Career Interest

```{r}
#| fig.height: 3.5
# converts the list into several columns
df23Int <- df23 %>% filter(Q14 == "Yes")
df23NotInt <- df23 %>% filter(Q14 == "No")

df23gInt <- tibble(
  "Barriers" = c("Physician Supply", "Physician Supply",
                 "Lack of Equipment", "Lack of Equipment",
                 "Lack of Payment", "Lack of Payment",
                 "Lack of Patient Education", "Lack of Patient Education",
                 "Language Barriers", "Language Barriers",
                 "Transportation Barriers", "Transportation Barriers",
                 "Infrastructure", "Infrastructure"),
  "Int_GH" = c("Yes", "No",
               "Yes", "No",
               "Yes", "No",
               "Yes", "No",
               "Yes", "No",
               "Yes", "No",
               "Yes", "No"),
  "Votes" = c(sum(df23Int$`Physician Supply`),
            sum(df23NotInt$`Physician Supply`),
            sum(df23Int$`Lack of Equipment`),
            sum(df23NotInt$`Lack of Equipment`),
            sum(df23Int$`Lack of Payment`),
            sum(df23NotInt$`Lack of Payment`),
            sum(df23Int$`Lack of Patient Education`),
            sum(df23NotInt$`Lack of Patient Education`),
            sum(df23Int$`Language Barriers`),
            sum(df23NotInt$`Language Barriers`),
            sum(df23Int$`Transportation Barriers`),
            sum(df23NotInt$`Transportation Barriers`),
            sum(df23Int$`Infrastructure`),
            sum(df23NotInt$`Infrastructure`))) %>%
  mutate(
    Decimal = as.double(if_else(Int_GH == "Yes",
                                Votes/nrow(df23Int),
                                Votes/nrow(df23NotInt))),
    Percent = percent(Decimal,accuracy = .1))

# barriers to healthcare in low resources by interest in Global Health
ggplot(df23gInt, aes(reorder(Barriers, -Votes), Votes, fill = Int_GH)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Barriers to Healthcare in low-resource settings", x = "",
       fill = "Interested in Global Health?", y = "") +
  geom_text(aes(label = Votes), vjust = -.2, position = position_dodge(width = .9)) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(limits = c(0,60)) +
  theme(axis.text.x = element_text(size = 7.3),
        legend.position = "bottom")
```

```{r}
#| fig.height: 3.5
ggplot(df23gInt, aes(reorder(Barriers, -Decimal), Decimal, fill = Int_GH)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Barriers to Healthcare in low-resource settings",
       x = "", fill = "Interested in Global Health?", y = "") +
  geom_text(aes(label = Percent), vjust = -.3,
            position = position_dodge(width = .9), size = 2.3) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1)
  ) +
  theme(axis.text.x = element_text(size = 7.3),
        legend.position = "bottom")
```

\newpage

Below is a Chi Squared Test. This tests to see if the two distributions of perceived barriers to low-resource healthcare are distinct from one another. The test cannot confirm that there is a distinction. In other words, the overall difference in perceived barriers to healthcare in low resource settings of those who are interested in a Global Health Career and those who are uninterested is not significant.

```{r}
#| warning: false
df23gIntChi <- df23gInt %>% select(Barriers, Int_GH, Percent) %>% 
  pivot_wider(names_from = Int_GH, values_from = Percent)
chisq.test(df23gIntChi$Yes, df23gIntChi$No)
```

\newpage

C. Barriers to Providing Healthcare by Born Abroad

```{r}
#| fig.height: 3.5
# converts the list into several columns
df23Born <- df23 %>% filter(Q10 == "Yes")
df23NotBorn <- df23 %>% filter(Q10 == "No")

df23gBorn <- tibble(
  "Barriers" = c("Physician Supply", "Physician Supply",
                 "Lack of Equipment", "Lack of Equipment",
                 "Lack of Payment", "Lack of Payment",
                 "Lack of Patient Education", "Lack of Patient Education",
                 "Language Barriers", "Language Barriers",
                 "Transportation Barriers", "Transportation Barriers",
                 "Infrastructure", "Infrastructure"),
  "Born_Abroad" = c("Yes", "No",
                    "Yes", "No",
                    "Yes", "No",
                    "Yes", "No",
                    "Yes", "No",
                    "Yes", "No",
                    "Yes", "No"),
  "Votes" = c(sum(df23Born$`Physician Supply`),
            sum(df23NotBorn$`Physician Supply`),
            sum(df23Born$`Lack of Equipment`),
            sum(df23NotBorn$`Lack of Equipment`),
            sum(df23Born$`Lack of Payment`),
            sum(df23NotBorn$`Lack of Payment`),
            sum(df23Born$`Lack of Patient Education`),
            sum(df23NotBorn$`Lack of Patient Education`),
            sum(df23Born$`Language Barriers`),
            sum(df23NotBorn$`Language Barriers`),
            sum(df23Born$`Transportation Barriers`),
            sum(df23NotBorn$`Transportation Barriers`),
            sum(df23Born$`Infrastructure`),
            sum(df23NotBorn$`Infrastructure`))) %>%
  mutate(
    Decimal = as.double(if_else(Born_Abroad == "Yes",
                                Votes/nrow(df23Born),
                                Votes/nrow(df23NotBorn))),
    Percent = percent(Decimal,accuracy = .1))

# barriers to healthcare in low resources by Born Abroad
ggplot(df23gBorn, aes(reorder(Barriers, -Votes), Votes, fill = Born_Abroad)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Barriers to Healthcare in low-resource settings", x = "",
       fill = "Born Abroad?", y = "") +
  geom_text(aes(label = Votes), vjust = -.2, position = position_dodge(width = .9)) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(limits = c(0,100)) +
  theme(axis.text.x = element_text(size = 7.3),
        legend.position = "bottom")
```

```{r}
#| fig.height: 3.5
ggplot(df23gBorn, aes(reorder(Barriers, -Decimal), Decimal, fill = Born_Abroad)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Barriers to Healthcare in low-resource settings",
       x = "", fill = "Born Abroad?", y = "") +
  geom_text(aes(label = Percent), vjust = -.3,
            position = position_dodge(width = .9), size = 2.3) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1)
  ) +
  theme(axis.text.x = element_text(size = 7.3),
        legend.position = "bottom")
```

\newpage

Below is a Chi Squared Test. This tests to see if the two distributions of perceived barriers to low-resource healthcare are distinct from one another. The test cannot confirm that there is a distinction. In other words, the overall difference in perceived barriers to healthcare in low resource settings of those who are interested in a Global Health Career and those who are uninterested is not significant.

```{r}
#| warning: false
df23gBornChi <- df23gBorn %>% select(Barriers, Born_Abroad, Percent) %>% 
  pivot_wider(names_from = Born_Abroad, values_from = Percent)
chisq.test(df23gBornChi$Yes, df23gBornChi$No)
```

\newpage

D. Barriers to Providing Healthcare by Lived Abroad

```{r}
#| fig.height: 3.5
# converts the list into several columns
df23Lived <- df23 %>% filter(Q12 == "Yes")
df23NotLived <- df23 %>% filter(Q12 == "No")

df23gLived <- tibble(
  "Barriers" = c("Physician Supply", "Physician Supply",
                 "Lack of Equipment", "Lack of Equipment",
                 "Lack of Payment", "Lack of Payment",
                 "Lack of Patient Education", "Lack of Patient Education",
                 "Language Barriers", "Language Barriers",
                 "Transportation Barriers", "Transportation Barriers",
                 "Infrastructure", "Infrastructure"),
  "Lived_Abroad" = c("Yes", "No",
                    "Yes", "No",
                    "Yes", "No",
                    "Yes", "No",
                    "Yes", "No",
                    "Yes", "No",
                    "Yes", "No"),
  "Votes" = c(sum(df23Lived$`Physician Supply`),
            sum(df23NotLived$`Physician Supply`),
            sum(df23Lived$`Lack of Equipment`),
            sum(df23NotLived$`Lack of Equipment`),
            sum(df23Lived$`Lack of Payment`),
            sum(df23NotLived$`Lack of Payment`),
            sum(df23Lived$`Lack of Patient Education`),
            sum(df23NotLived$`Lack of Patient Education`),
            sum(df23Lived$`Language Barriers`),
            sum(df23NotLived$`Language Barriers`),
            sum(df23Lived$`Transportation Barriers`),
            sum(df23NotLived$`Transportation Barriers`),
            sum(df23Lived$`Infrastructure`),
            sum(df23NotLived$`Infrastructure`))) %>%
  mutate(
    Decimal = as.double(if_else(Lived_Abroad == "Yes",
                                Votes/nrow(df23Lived),
                                Votes/nrow(df23NotLived))),
    Percent = percent(Decimal,accuracy = .1))

# barriers to healthcare in low resources by Lived Abroad
ggplot(df23gLived, aes(reorder(Barriers, -Votes), Votes, fill = Lived_Abroad)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Barriers to Healthcare in low-resource settings", x = "",
       fill = "Lived Abroad?", y = "") +
  geom_text(aes(label = Votes), vjust = -.2, position = position_dodge(width = .9)) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(limits = c(0,100)) +
  theme(axis.text.x = element_text(size = 7.3),
        legend.position = "bottom")
```

```{r}
#| fig.height: 3.5
ggplot(df23gLived, aes(reorder(Barriers, -Decimal), Decimal, fill = Lived_Abroad)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Barriers to Healthcare in low-resource settings",
       x = "", fill = "Lived Abroad?", y = "") +
  geom_text(aes(label = Percent), vjust = -.3,
            position = position_dodge(width = .9), size = 2.3) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1)
  ) +
  theme(axis.text.x = element_text(size = 7.3),
        legend.position = "bottom")
```

\newpage

Below is a Chi Squared Test. This tests to see if the two distributions of perceived barriers to low-resource healthcare are distinct from one another. The test cannot confirm that there is a distinction. In other words, the overall difference in perceived barriers to healthcare in low resource settings of those who are interested in a Global Health Career and those who are uninterested is not significant.

```{r}
#| warning: false
df23gLivedChi <- df23gLived %>% select(Barriers, Lived_Abroad, Percent) %>% 
  pivot_wider(names_from = Lived_Abroad, values_from = Percent) %>% view()
chisq.test(df23gLivedChi$Yes, df23gLivedChi$No)
```

\newpage

## 12. Rank the following in order of the medical field that you believe has historically had the GREATEST impact on the global health field to the medical field you believe has historically had the LEAST impact on the global health field.

```{r}
# creating the column names vector
df24c <- df0 %>%
  filter((Q24_1 != "")) %>%
  select(starts_with("Q24_")) %>%
  slice(1) %>% t() %>% as.data.frame()
FieldsL <- str_replace(df24c$V1, "Rank the following in order of the medical field that you believe has historically had the GREATEST impact on the global health field to the medical field you believe has historically had the LEAST impact on the global health field. - ", "") %>%
  recode("OB/GYN (including maternal fetal medicine)" = "OB/GYN",
         "Surgical care (elective, urgent & obstetric)" = "Surgical care")

FieldsL <- unlist(FieldsL)

# tidying up the data
df24 <- df0 %>%
  filter((Q24_1 != "")) %>%
  select(starts_with("Q24_")) %>%
  slice(3:n())

# renaming the columns
colnames(df24) <- FieldsL

df24 <- df24 %>% mutate_all(
    function(x) as.numeric(as.character(x))
    ) %>%
      pivot_longer(c(`Emergency medicine`:`Orthopedics`),
                   names_to = "Fields", values_to = "Rank")

# creating summary
df24s <- df24 %>%
  group_by(Fields) %>%
  summarize(
    Minimum = min(Rank),
    "Q-1" = quantile(Rank, .25),
    Mean = mean(Rank),
    "Q-3" = quantile(Rank, .75),
    Maximum = max(Rank)
  ) %>%
  arrange(Mean) %>% print()

# order
Fields24Order <- df24s %>% select(Fields)
```

\newpage

```{r}
#| fig.height: 8.5
#| fig.width: 7
ggplot(df24) +
  geom_histogram(aes(Rank, fill = Fields), binwidth = 1) +
  facet_wrap(~Fields, scales = 'free_x') +
  theme(legend.position = "none") +
  labs(title = "Medical Field Historical Impact Rankings", y = "", x = "") +
  scale_x_continuous(breaks = seq(1, 11, by = 2))
```

\newpage

## 13. Rank the following in order of the medical field that you believe will have the GREATEST impact on the global health field in the future to the medical field you believe will have the LEAST impact on the global health field in the future.

```{r}
# creating the column names vector
df25c <- df0 %>%
  filter((Q25_1 != "")) %>%
  select(starts_with("Q25_")) %>%
  slice(1) %>% t() %>% as.data.frame()
FieldsL <- str_replace(df25c$V1, "Rank the following in order of the medical field that you believe will have the GREATEST impact on the global health field in the future to the medical field you believe will have the LEAST impact on the global health field in the future. - ", "") %>%
  recode("OB/GYN (including maternal fetal medicine)" = "OB/GYN",
         "Surgical care (elective, urgent & obstetric)" = "Surgical care")

FieldsL <- unlist(FieldsL)

# tidying up the data
df25 <- df0 %>%
  filter((Q25_1 != "")) %>%
  select(starts_with("Q25_")) %>%
  slice(3:n())

# renaming the columns
colnames(df25) <- FieldsL

df25 <- df25 %>% mutate_all(
    function(x) as.numeric(as.character(x))
    ) %>%
      pivot_longer(c(`Emergency medicine`:`Orthopedics`),
                   names_to = "Fields", values_to = "Rank")

# creating summary
df25s <- df25 %>%
  group_by(Fields) %>%
  summarize(
    Minimum = min(Rank),
    "Q-1" = quantile(Rank, .25),
    Mean = mean(Rank),
    "Q-3" = quantile(Rank, .75),
    Maximum = max(Rank)
  ) %>%
  arrange(Mean) %>% print()
```

\newpage

```{r}
#| fig.height: 8.5
#| fig.width: 7
ggplot(df25) +
  geom_histogram(aes(Rank, fill = Fields), binwidth = 1) +
  facet_wrap(~Fields, scales = 'free_x') +
  theme(legend.position = "none") +
  labs(title = "Medical Field Impact Rankings", y = "", x = "") +
  scale_x_continuous(breaks = seq(1, 11, by = 2))
```



\newpage

## 14. In your opinion, which THREE of the following medical fields contribute MOST to strengthening the delivery of all other types of care?

A. Overall Results for Contribution of Various Medical Fields to other types

```{r}
df27 <- df %>%
  filter(Q27 != "") %>%
  mutate(
    "Emergency Medicine" = str_count(Q27, "Emergency medicine"),
    "Family Medicine" = str_count(Q27, "Family medicine"),
    "Infectious Diseases" = str_count(Q27, "Infectious Diseases"),
    "Neurology" = str_count(Q27, "Neurology"),
    "OB/GYN" = str_count(Q27, "OB/GYN"),
    "Oncology" = str_count(Q27, "Oncology"),
    "Pediatrics" = str_count(Q27, "Pediatrics"),
    "Psychiatry" = str_count(Q27, "Psychiatry"),
    "Surgical Care" = str_count(Q27, "Surgical care"),
    "Ophthalmology" = str_count(Q27, "Ophthalmology"),
    "Orthopedics" = str_count(Q27, "Orthopedics"),
    "Number of Fields Selected" = str_count(Q23, ",") + 1
  )

# creates a tibble of the totals
df27g <- tibble(
  "Fields" = c("Emergency Medicine", "Family Medicine",
               "Infectious Diseases", "Neurology",
               "OB/GYN", "Oncology",
               "Pediatrics", "Psychiatry",
               "Surgical Care", "Ophthalmology",
               "Orthopedics"),
  "Votes" = c(sum(df27$`Emergency Medicine`),
              sum(df27$`Family Medicine`),
              sum(df27$`Infectious Diseases`),
              sum(df27$`Neurology`),
              sum(df27$`OB/GYN`),
              sum(df27$`Oncology`),
              sum(df27$`Pediatrics`),
              sum(df27$`Psychiatry`),
              sum(df27$`Surgical Care`),
              sum(df27$`Ophthalmology`),
              sum(df27$`Orthopedics`))) %>%
  mutate(
    "Unselected" = nrow(df23) - Votes,
    "Percent" = percent((Votes / nrow(df23)), accuracy = .1)
  )
# creates a barplot of each of the perceived barriers to Global Health
# and includes percent selected
ggplot(df27g, aes(reorder(Fields, -Votes), Votes)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Medical Fields that strengthen other types of care",
       x = "", y = "") +
  geom_text(aes(label = Percent), nudge_y = 5) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  theme(axis.text.x = element_text(size = 5.6)) +
  scale_y_continuous(limits = c(0,95))
```


\newpage

## 15. Increasing access to surgical care should be a priority for countries increasing access to healthcare.

A. Overall Results

```{r}
Response_levels <- c("Strongly Agree", "Agree", "Undecided", "Disagree", "Strongly Disagree")
df28 <- df %>% filter(Q28 != "") %>%
  mutate(
    factor(Q28, levels = Response_levels)
  )
# Bar Graph
df28 %>%
  group_by(Q28) %>%
  summarise(
    Count = n()
  ) %>% add_row(
    Q28 = "Strongly Disagree", Count = 0
  ) %>%
  ggplot(aes(fct_relevel(Q28, Response_levels), Count)) +
  geom_bar(stat = "identity", fill = "cornsilk3") +
  geom_text(aes(label = signif(Count)), nudge_y = 3) +
  labs(title = "Prioritize Increasing Access to Surgical Care",
       x = "", y = "") +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 13))
```



