---
format: 
  pdf:
    keep-tex: true
editor_options: 
  chunk_output_type: console
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#", fig.height = 3, 
  cache = FALSE,  collapse = TRUE,
  error = TRUE, echo = FALSE,
  message = FALSE
)
```

<!-- put your name below instead of mine -->

Caleb Skinner

Global Health Survey Questions 6-10

<!-- Setting up tidyverse. Reading in the csv and all that bonkers stuff -->
```{r}
#| include: false
library("here")
library("tidyverse"); theme_set(theme_minimal())
library(rjags)
library(rstanarm)
library(scales)
library(ggpubr)
library(broom)
library(AICcmodavg)
library(waffle)
library(gtsummary)

# loading df- helpful for viewing the questions
file_name <- here("Global_Health_data.csv")
df0 <- read_csv(file_name) %>%
  select(20,22:24,26,28,30,36,38:45,47:50, 73:74) # %>% view()
# The ranked ones are from 51-72

# removing excess rows and fixing bad responses
df <- df0[-c(1:2),] %>% 
  mutate(Q17 = recode(Q17,
                      'Strongly Agree ' = 'Strongly Agree',
                      'Undecided ' = 'Undecided',
                      'Strongly Disagree ' = 'Strongly Disagree'),
         Q22 = recode(Q22,
                      'Strongly Agree ' = 'Strongly Agree',
                      'Undecided ' = 'Undecided',
                      'Strongly Disagree ' = 'Strongly Disagree'),
         Q14 = recode(Q14,
                      'No ' = 'No'),
         Q13 = recode(Q13,
                      '15+ years ' = '15+ years',
                      '5 - 10 years ' = '5 - 10 years',
                      '10 - 15 years ' = '10 - 15 years',
                      '1 - 5 years ' = '1 - 5 years',
                      'Less than one year ' = 'Less than one year'
         ),
         Q6 = recode(Q6,
                     'Pre-professional track - only choose this option if you do not have another major that fits into one of the above categories' = 'Pre-Professional Track'),
         Q18 = recode(Q18,
                      'I don’t know' = "I don't know")
  )
```

## Questions:

## 6. In your opinion, are there enough global health opportunities available to US pre-medical students?

A. Overall Results for Global Health Opportunities Availability.

```{r}
YNResponses <- c("Yes", "I don't know", "No")
df18 <- df %>% 
  filter(Q18 != "") %>% mutate(
    factor(Q18, YNResponses)
  )

df18ttest <- df18 %>%
  mutate(Q18 = case_when(
    Q18 == "I don't know" ~ .5,
    Q18 == "Yes" ~ 1,
    Q18 == "No" ~ 0)
  )

df18 %>%
  group_by(Q18) %>%
  summarise(
    Counts = n()
  ) %>% ggplot(aes(fct_relevel(Q18, YNResponses), Counts)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Are there enough global health opportunities?", x = "", y = "") +
  geom_text(aes(label = signif(Counts)), nudge_y = 3)
```

\newpage

B. Global Health Opportunities by Global Health Career Interest

```{r}
df18Int <- df18 %>%
  filter(Q14 != "") %>% 
  group_by(Q14, Q18) %>%
  summarise(
    Count = n()
  )
ggplot(df18Int, aes(Q14, Count, fill = fct_relevel(Q18, YNResponses))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Opportunities in Global Health by Global Health Interest",
       x = "Global Health Career Interest",
       fill = "Enough Global Health Opportunities:", y = "") +
  theme(legend.position = "bottom") +
  geom_text(aes(label = signif(Count)), vjust = -.1, position = position_dodge(width = .9)) +
  scale_y_continuous(limit = c(0, 43))
```

```{r}
df18Int %>% group_by(Q14) %>%
  mutate(
    Decimal = Count / sum(Count),
    Percent = percent(Decimal, accuracy = .1)
  ) %>%
  ggplot(aes(reorder(Q14, Count), Decimal,
             fill = fct_relevel(Q18, YNResponses))) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 11)) +
  labs(title = "Opportunities in Global Health by Global Health Interest",
       x = "Global Health Career Interest",
       fill = "Enough Global Health Opportunities:",
       y = "") +
  theme(legend.position = "bottom") +
  geom_text(aes(label = Percent), vjust = -.1,
            position = position_dodge(width = .9),
            size = 3) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1),
    limits = c(0,.65)
  )
```

\newpage

The following is a t-test measuring the difference in belief that there are sufficient Global Health opportunities for pre-med students in those who have expressed interest in a Global Health Career and those who have not. For this t-test, I counted "I don't know" responses to the sufficient Global Health Opportunities Question as 1/2 a "yes" and 1/2 a "no".
The results are significant. Those who have express an interest in a Global Health Career indicate that there are not sufficient Global Health Opportunities at a higher rate than those who have not expressed an interest in a Global Health Career.

```{r}
t.test(df18ttest %>% filter(Q14 == "No") %>% select(Q18),
       df18ttest %>% filter(Q14 == "Yes") %>% select(Q18))
```

The following is a second t-test measuring the difference in belief that there are sufficient Global Health opportunities for pre-med students in those who have expressed interest in a Global Health Career and those who have not. For this t-test, I removed all "I don't know" responses.
The results are not significant. This is likely because a large amount of respondents selected "I don't know." This drops the sample size to only 80.

```{r}
t.test(df18ttest %>% filter(Q14 == "No", Q18 != .5) %>% select(Q18),
       df18ttest %>% filter(Q14 == "Yes", Q18 != .5) %>% select(Q18))
```

\newpage

## 7. Which, if any, of the following do you perceive as reasons it is difficult for undergraduate pre-medical students to learn more about global health and gain experience in the field prior to medical school?

```{r}
df19 <- df %>% filter(Q19 != "") %>% mutate(
  Faculty = str_count(Q19, "Lack of global health faculty"),
  Extracurricular = str_count(Q19, "Lack of extracurricular opportunities"),
  Busyness = str_count(Q19, "Time constraints"),
  Financial = str_count(Q19, "Financial barriers"),
  Research = str_count(Q19, "research opportunities"),
  Ethical_Issues = str_count(Q19, "Ethical issues"),
  Physician_Mentorship = str_count(Q19, "Lack of mentorship"),
  Other = str_count(Q19, "Other"),
  Total_Problems = rowSums(across(where(is.numeric)))
) %>% view()
df19g <- df19 %>% summarise(
  'Lacking Faculty Mentorship' = sum(Faculty),
  'Lacking Extracurricular Opportunities' = sum(Extracurricular),
  Busyness = sum(Busyness),
  Financial = sum(Financial),
  'Lacking Research Opportunities' = sum(Research),
  'Ethical Issues' = sum(Ethical_Issues),
  'Lacking Physician Mentorship' = sum(Physician_Mentorship),
  Other = sum(Other)
) %>%
  t() %>% as.data.frame() %>% rownames_to_column(var = "rowname") # %>% view()
colnames(df19g) <- c("Problems", "Count")
df19g <- df19g %>% mutate(
  Percent = percent(Count/nrow(df %>% filter(Q19 != "")), accuracy = .1)
) # %>% view()

# creates a barplot of each of the academic disciplines for education training
# and includes percent selected
ggplot(df19g, aes(reorder(Problems, -Count), Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Hindrances to Global Health Awareness and Experience",
       x = "Hindrances", y ="") +
  geom_text(aes(label = Percent), nudge_y = 5.5) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 12)) +
  scale_y_continuous(limit = c(0,140)) +
  theme(axis.text.x = element_text(size = 6.8))
```

```{r}
df19 %>% group_by(Total_Problems) %>%
  summarise(
    Count = n()
  ) %>% 
  ggplot(aes(Total_Problems, Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Total Hindrances to Global Health", x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 2) +
  scale_x_continuous(breaks = seq(1,9, by = 1))
```

\newpage

## 8. What do you think should be required for pre-medical students to engage in clinical global health work and/or mission trips?

```{r}
df20 <- df %>% filter(Q20 != "") %>% mutate(
  Clinical_Certification = str_count(Q20, "clinical certification"),
  Cultural_Education = str_count(Q20, "Education on the community"),
  Local_Language = str_count(Q20, "Knowledge of the local language"),
  Medical_Ethics = str_count(Q20, "Medical ethics education"),
  Volunteer_Experience = str_count(Q20, "volunteer experience"),
  Nonclinical_role = str_count(Q20, "non-clinical role on the mission trip"),
  No_Undergrad_Mission_Trips = str_count(Q20, "Undergraduates should never"),
  Total_Conditions = rowSums(across(where(is.numeric)))
) # %>% view()
df20g <- df20 %>% summarise(
  "Clinical Certification" = sum(Clinical_Certification),
  "Cultural Education" = sum(Cultural_Education),
  "Local Language Training" = sum(Local_Language),
  "Medical Ethics Education" = sum(Medical_Ethics),
  "Volunteer Experience" = sum(Volunteer_Experience),
  "Non-clinical role on mission trip" = sum(Nonclinical_role),
  "Undergraduates should not engage in Mission Trips" = sum(No_Undergrad_Mission_Trips)
) %>%
  t() %>% as.data.frame() %>% rownames_to_column(var = "rowname") %>% view()
colnames(df20g) <- c("Conditions", "Count")
df20g <- df20g %>% mutate(
  Percent = percent(Count/nrow(df %>% filter(Q19 != "")), accuracy = .1)
)
# creates a barplot of each of the conditions to engage in global health work/mission trip
# and includes percent selected
ggplot(df20g, aes(reorder(Conditions, -Count), Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Requirements for pre-medical students to engage in 
         clinical global health work and/or mission trips", x = "Requirements", y = "") +
  geom_text(aes(label = Percent), nudge_y = 5, size = 3.1) +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 15)) +
  scale_y_continuous(limits = c(0,120)) +
  theme(axis.text.x = element_text(size = 7))
```

```{r}
df20 %>% group_by(Total_Conditions) %>%
  summarise(
    Count = n()
  ) %>% 
  ggplot(aes(Total_Conditions, Count)) +
  geom_bar(stat = "identity", fill = 'cornsilk3') +
  labs(title = "Conditions Needed to engage in Global Health Work/Missions",
       x = "", y = "") +
  geom_text(aes(label = signif(Count)), nudge_y = 2.5) +
  scale_x_continuous(breaks = seq(1,9, by = 1)) +
  scale_y_continuous(limits = c(0,60))
```

\newpage

## 9. Short-term mission trips are an effective way to address global health challenges.

A. Overall Results

```{r}
Response_levels <- c("Strongly Agree", "Agree", "Undecided", "Disagree", "Strongly Disagree")
df21 <- df %>% filter(Q21 != "") %>%
  mutate(
    factor(Q21, levels = Response_levels)
  )
# Bar Graph
df21 %>%
  group_by(Q21) %>%
  summarise(
    Count = n()
  ) %>%
  ggplot(aes(fct_relevel(Q21, Response_levels), Count)) +
  geom_bar(stat = "identity", fill = "cornsilk3") +
  geom_text(aes(label = signif(Count)), nudge_y = 3) +
  labs(title = "Short-term mission trips are effective",
       x = "", y = "") +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 13))
```

\newpage

B. Effectiveness of Mission Trips by Lived Abroad

```{r}
df21gLive <- df21 %>%
  filter(Q12 != "") %>% 
  group_by(Q12, Q21) %>%
  summarise(
    Count = n()
  ) # %>% view()
ggplot(df21gLive, aes(Q12, Count, fill = fct_relevel(Q21, Response_levels))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Effectiveness of Short-term missions by Lived Abroad",
       x = "Lived Abroad",
       fill = "Missions are Effective:", y = "") +
  theme(legend.position = "bottom", legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) +
  geom_text(aes(label = signif(Count)), vjust = -.1,
            position = position_dodge(width = .9)) +
  scale_y_continuous(limits = c(0, 60))
```

```{r}
df21gLive %>% group_by(Q12) %>%
  mutate(
    Decimal = Count / sum(Count),
    Percent = percent(Decimal, accuracy = .1)
  ) %>%
  ggplot(aes(Q12, Decimal, fill = fct_relevel(Q21, Response_levels))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Effectiveness of Short-term missions by Lived Abroad",
       x = "Lived Abroad",
       fill = "Missions are Effective:", y = "") +
  theme(legend.position = "bottom", legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) +
  geom_text(aes(label = Percent), vjust = -.1,
            position = position_dodge(width = .9), size = 2.5) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1)
  )
```

\newpage

C. Effectiveness of Mission Trips by Born Abroad

```{r}
df21gBorn <- df21 %>%
  filter(Q10 != "") %>% 
  group_by(Q10, Q21) %>%
  summarise(
    Count = n()
  ) # %>% view()
ggplot(df21gBorn, aes(Q10, Count, fill = fct_relevel(Q21, Response_levels))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Effectiveness of Short-term missions by Born Abroad",
       x = "Born Abroad",
       fill = "Missions are Effective:", y = "") +
  theme(legend.position = "bottom", legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) +
  geom_text(aes(label = signif(Count)), vjust = -.1,
            position = position_dodge(width = .9)) +
  scale_y_continuous(limits = c(0, 60))
```

```{r}
df21gBorn %>% group_by(Q10) %>%
  mutate(
    Decimal = Count / sum(Count),
    Percent = percent(Decimal, accuracy = .1)
  ) %>%
  ggplot(aes(Q10, Decimal, fill = fct_relevel(Q21, Response_levels))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Effectiveness of Short-term missions by Lived Abroad",
       x = "Lived Abroad",
       fill = "Missions are Effective:", y = "") +
  theme(legend.position = "bottom", legend.title = element_text(size = 7),
        legend.text = element_text(size = 7)) +
  geom_text(aes(label = Percent), vjust = -.1,
            position = position_dodge(width = .9), size = 2.5) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1)
  )
```

\newpage

## 10. Practicing clinical medicine is the most important aspect of global health.

A. Overall Results

```{r}
df22 <- df %>% filter(Q22 != "") %>%
  mutate(
    factor(Q22, levels = Response_levels)
  )
# Bar Graph
df22 %>%
  group_by(Q22) %>%
  summarise(
    Count = n()
  ) %>%
  ggplot(aes(fct_relevel(Q22, Response_levels), Count)) +
  geom_bar(stat = "identity", fill = "cornsilk3") +
  geom_text(aes(label = signif(Count)), nudge_y = 3) +
  labs(title = "Practicing clinical medicine is the most important part of Global Health",
       x = "", y = "") +
  scale_x_discrete(labels = function(x) str_wrap(x,width = 13))
```

\newpage

B. Importance of Clinical Medicine by Major

```{r}
#| fig-height: 4
df22gLive <- df22 %>%
  filter(Q6 != "") %>% 
  group_by(Q6, Q22) %>%
  summarise(
    Count = n()
  ) %>% group_by(Q6) %>%
  mutate(
    Decimal = Count / sum(Count),
    Percent = percent(Decimal, accuracy = .1)
  )
ggplot(df22gLive, aes(reorder(Q6, -Count), Decimal, fill = fct_relevel(Q22, Response_levels))) +
  geom_bar(stat = "identity", position = position_stack()) +
  labs(title = "Importance of Clinical Medicine by Major",
       x = "", fill = "Clinical Medicine is Important: ", y = "") +
  theme(legend.position = "bottom", legend.title = element_text(size = 6),
        legend.text = element_text(size = 5.5),
        axis.text.x = element_text(size = 7)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 12)) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1),
  )
```

\newpage

C. Importance of Clinical Medicine by Global Health Interest

```{r}
df22gInt <- df22 %>%
  filter(Q12 != "") %>% 
  group_by(Q12, Q22) %>%
  summarise(
    Count = n()
  ) # %>% view()
ggplot(df22gInt, aes(Q12, Count, fill = fct_relevel(Q22, Response_levels))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Importance of Clinical Medicine by Global Health Interest",
       x = "Interest in a Global Health Career",
       fill = "Clinical Medicine is Important:", y = "") +
  theme(legend.position = "bottom", legend.title = element_text(size = 6),
        legend.text = element_text(size = 5.5)) +
  geom_text(aes(label = signif(Count)), vjust = -.1,
            position = position_dodge(width = .9)) +
  scale_y_continuous(limits = c(0, 50))
```

```{r}
df22gInt %>% group_by(Q12) %>%
  mutate(
    Decimal = Count / sum(Count),
    Percent = percent(Decimal, accuracy = .1)
  ) %>%
  ggplot(aes(Q12, Decimal, fill = fct_relevel(Q22, Response_levels))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Importance of Clinical Medicine by Global Health Interest",
       x = "Interest in a Global Health Career",
       fill = "Clinical Medicine is Important:", y = "") +
  theme(legend.position = "bottom", legend.title = element_text(size = 6),
        legend.text = element_text(size = 5.5)) +
  geom_text(aes(label = Percent), vjust = -.2,
            position = position_dodge(width = .9), size = 2.5) +
  scale_y_continuous(
    breaks = seq(0, 1, by = .10),
    labels = label_percent(accuracy = 1)
  )
```
